\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip Transmission of respiratory viral infections with and without air cleaners in a Swiss school under non-pandemic conditions in 2023: A modeling study of epidemiological, environmental, and molecular data}

### 2023-10-16 doc/paper/supplements.tex
Updates from Overleaf

% author list
\author[1$\ddag$,2]{Nicolas Banholzer}
\author[2,3]{Philipp Jent}
\author[2,4]{Pascal Bittel}
\author[1]{Kathrin Zürcher}
\author[4]{Lavinia Furrer}
\author[1]{Simon Bertschinger}
\author[2,4]{Alban Ramette}
\author[2,4]{Ronald Dijkman}
\author[1]{Matthias Egger}
\author[2,5]{Tina Hascher}
\author[1*,2]{Lukas Fenner}

@@

@@

@@

\begin{figure}[!htb]
\centering
    \includegraphics[width=\linewidth]{../../results/env-data/otherVars-boxplot.pdf}
    \caption[Boxplot of environmental variables by school and study condition]{Boxplot for the daily average values of each environmental variable by school and study condition.}
    \label{fig:env-descriptives-other-vars}
\end{figure}

\begin{table}[!htpb]
    \caption[Estimated reduction in aerosol and particle concentrations with interventions]{Estimated reduction in aerosol number (CN) and particle mass (PM) concentrations with interventions (posterior mean and upper and lower estimate from the 95\%-CrI).}
    \label{tab:palas-est-results}
    \centering
    \footnotesize
    \begin{tabular}{l r r r}
    \toprule
    Variable & Mean & Lower & Upper \\
    \midrule
    \input ../../results/env-data/estimation-results-table.tex
    \bottomrule
    \end{tabular}

\end{table}

>>>>

% author list
\author[1$\ddag$,2]{Nicolas Banholzer}
\author[2,3]{Philipp Jent}
\author[2,4]{Pascal Bittel}
\author[1]{Kathrin Zürcher}
\author[4]{Lavinia Furrer}
\author[1]{Simon Bertschinger}
\author[2,4]{Alban Ramette}
\author[2,4]{Ronald Dijkman}
\author[1]{Matthias Egger}
\author[5]{Tina Hascher}
\author[1*,2]{Lukas Fenner}

@@

Our estimation results imply a small, potential benefit of air cleaners. Subject to considerable uncertainty, \Cref{fig:avoided-infections} shows the estimated number number of infections that would have occurred if air cleaners had been installed throughout the study (scenario~1) or not been installed (scenario~2).

\begin{figure}[!htpb]
    \includegraphics{../../results/epi-data/avoided-infections.pdf}
    \caption[Estimated number of infections with and without air cleaners]{Estimated mean number of infections (posterior mean as dot and 50\%, 80\%, and 95\%-CrI as shaded areas) if, in both classes, air cleaners had been installed throughout the study or not been installed.}
    \label{fig:avoided-infections}
\end{figure}

@@

There was a strong difference in particle concentrations between study conditions (\Cref{fig:palas-results}a). When adjusting for air change rates and multiple other factors, the aerosol number concentration decreased by 76\% (95\%-CrI 63\% to 86\%) with air cleaners (\Cref{fig:palas-results}b and \Cref{tab:palas-est-results}). The decrease in the concentration of larger particles (PM$_{10}$) was greater than the decrease in the concentration of smaller particles (PM$_1$ to PM$_{4}$).

\begin{figure}[!htpb]
\centering
    \includegraphics[width=\linewidth]{../../results/env-data/particles-boxplot.pdf}
    \includegraphics[width=\linewidth]{../../results/env-data/estimation-results-figure.pdf}
    \caption[Analysis of particle concentrations and comparison between study conditions]{\textbf{Analysis of particle concentrations and comparison between study conditions}. \textbf{(a)}~Boxplot of the daily average values for aerosol number concentration (CN in 1/cm$^3$) and particle mass concentration (PM for particles of sizes <1 to <10~$\mu$m, respectively in $\mu$gm$^{-3}$). \textbf{(b)}~Estimated reduction in aerosol number and particle mass concentrations with air cleaners (posterior mean as dot and 50\%-, 80\%- and 95\%-CrI as lines, respectively). }
    \label{fig:palas-results}
\end{figure}

\begin{table}[!htpb]
    \caption[Estimated reduction in aerosol and particle concentrations with interventions]{Estimated reduction in aerosol number (CN) and particle mass (PM) concentrations with interventions (posterior mean and upper and lower estimate from the 95\%-CrI).}
    \label{tab:palas-est-results}
    \centering
    \footnotesize
    \begin{tabular}{l r r r}
    \toprule
    Variable & Mean & Lower & Upper \\
    \midrule
    \input ../../results/env-data/estimation-results-table.tex
    \bottomrule
    \end{tabular}
\end{table}

@@

\begin{figure}[!htb]
\centering
    \includegraphics[width=\linewidth]{../../results/env-data/otherVars-boxplot.pdf}
    \caption[Boxplot of environmental variables by study condition]{Boxplot for the daily average values of each environmental variable by study condition.}
    \label{fig:env-descriptives-other-vars}
\end{figure}

\section{Detailed results for cough frequency}\label{sec:detailed-results-coughing}

Differences in the frequency of coughs between classes suggest an association with class-specific virus patterns. \Cref{fig:coughing-association} shows the relative risk of cough for each respiratory virus. Cough appeared more frequent for Flu~B and less frequent for AdV.

\begin{figure}[!htpb]
    \centering
    \includegraphics{results/cough-data/coughs-virus-association.pdf}
    \caption[Association between cough frequency and virus-specific positivity rate]{Estimated association (relative risk; posterior mean as dot, 50\%, 80\%, and 95\%-CrI as lines) between cough frequency and number of positive saliva test results by respiratory virus. Flu B: Influenza B, HRV: rhinovirus, AdV: adenovirus, CoV: SARS-CoV-2, MPV: metapneumovirus, PIV: parainfluenza virus.}
    \label{fig:coughing-association}
\end{figure}
